State of the Practice of Lattice Boltzmann Method Software Development

### 2021-06-21 StateOfPractice/Peter-Notes/Report/Report.tex
fixed some typos LBM Report

This report analyzes the development of software packages that use Lattice Boltzmann Methods (LBM), a class of computational fluid dynamics (CFD) methods, for fluid simulation. These LBM algorithms consider the behaviours of a collection of particles as a single unit of an intermediate size, and predict their positional probability as they move through a lattice structure. Figure \ref{circularflow} from \citep{chen2021phase} presents the streamlines of converged flow past a stationary circular cylinder with varied Raynolds number, a common task of LBM.

@@

This report analyzes a filtered set of LBM software packages along quantitative and qualitative measures. Many of these measures are captured using surface measurements, which can be categorized as initial and easy to capture measurements, of the underlying quality; they may not represent the true quality of the software. Surface measurements are taken as they allow us to apply the same measurement, with reasonable effort, along all software packages despite technical and functional variabilities among the set of software packages. Not all qualities are quantitatively measured. For example, performance is not measured by running the code. A surface investigation of the documentation of each software package for performance information is conducted instead. The measured software packages are open source, and it is recommended to keep this in mind when considering the recommendations of this report. Some recommendations may not apply to closed-source software. Practices surrounding close source software development may differ.

@@

Interviews suggested a more frequent use of both unit testing and continuous integration in the development processes than what was observed from the artifact survey. For example, OpenLB, pyLBM, and TCLB use such methods during development despite this not being explicitly clear from an analysis of the material available online. The correctness and verificablity of such packages is not measured well using surface analysis.

>>>>

We analyze the development of software packages that use Lattice Boltzmann Methods (LBM), a class of computational fluid dynamics (CFD) methods, for fluid simulation. These LBM algorithms consider the behaviours of a collection of particles as a single unit of an intermediate size, and predict their positional probability as they move through a lattice structure. Figure \ref{circularflow} from \citep{chen2021phase} presents the streamlines of converged flow past a stationary circular cylinder with varied Reynolds number, a common task of LBM.

@@

We analyze a filtered set of LBM software packages along quantitative and qualitative measures. Many of these measures are captured using surface measurements, which can be categorized as initial and easy to capture measurements, of the underlying quality; they may not represent the true quality of the software. Surface measurements are taken as they allow us to apply the same measurement, with reasonable effort, along all software packages despite technical and functional variabilities among the set of software packages. Not all qualities are quantitatively measured. For example, performance is not measured by running the code. A surface investigation of the documentation of each software package for performance information is conducted instead. The measured software packages are open source, and it is recommended to keep this in mind when considering the recommendations of this report. Some recommendations may not apply to closed-source software. Practices surrounding close source software development may differ.

@@

Interviews suggested a more frequent use of both unit testing and continuous integration in the development processes than what was observed from the initial survey. For example, OpenLB, pyLBM, and TCLB use such methods during development despite this not being explicitly clear from an analysis of the material available online. The correctness and verificablity of such packages is not measured well using surface analysis.
